Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
added bullet point for the EM

	\item so when we have joint state parameter estimation for stae-space models  we only need to do two things: 1- use smoother for the E-step 2- construct the lower bound which might not be straightforward even in linear case

>>>>

	\item so when we have joint state parameter estimation for stae-space models  we only need to do two things: 1- use smoother for the E-step 2- construct the lower bound which might not be straightforward even in linear case so DCM is rubbish
